Scheduling and Amortization for MPC

### 2021-02-08 chapterfour/introduction.tex
Made chapterfour.tex standalone.

Researchers have proposed different encryption schemes to support 
a variety of operations, allowing for larger and larger subsets of
programs to be run this way. Again, Fully Homomorphic Encryption (FHE) \cite{Gentry:2010},\cite{Gentry:20102}  
can perform arbitrary operations on encrypted data, but in its current state FHE
is still prohibitively expensive \cite{Gentry:2011}. An alternative to FHE 
is Partially Homomorphic Encryption (PHE), which scales substantially better, but cannot 
perform arbitrary operations, and requires the conversions that were discussed in \chapref{chapter:chapterthree}.

>>>>

Researchers have proposed different encryption schemes to support 
a variety of operations, allowing for larger and larger subsets of
programs to be run this way. Again, Fully Homomorphic Encryption (FHE) \cite{Gentry:2010},\cite{Gentry:20102}  
can perform arbitrary operations on encrypted data, but in its current state FHE
is still prohibitively expensive \cite{Gentry:2011}. An alternative to FHE 
is Partially Homomorphic Encryption (PHE), which scales substantially better, but cannot 
perform arbitrary operations, and requires the conversions. %that were discussed in \chapref{chapter:chapterthree}.

### 2021-02-08 chapterfour/overview.tex
Made chapterfour.tex standalone.

\begin{figure}[h]
\centering
\begin{minipage}{0.7\textwidth}
% \begin{figure}[h]
\begin{javacode}
int sq_arr(int A[]) {
    for(int i = 0; i < A.length; i++) {
        A[i] = A[i] * A[i];
    }
    return A;
}
\end{javacode}
% \end{figure}
\end{minipage}
\caption{Code to square each member of an array.}
\label{fig:squarearray}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{0.7\textwidth}
% \begin{figure}[h]
\begin{javacode}
int sq_arr(Share A[]) {
    B = MUL_N(A, A);
    return B;
}
\end{javacode}
% \end{figure}
\end{minipage}
\caption{Simple MPC transformation to square an array.}
\label{fig:squarearraympc}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{minipage}{0.7\textwidth}
% \begin{figure}[h]
\begin{code}
int sq\_arr(int A[]) {
    for(int i = 0; i < A.length; i++) {
        A[i] = A[i] * A[i];
    }
    return A;
}
\end{code}
% \end{figure}
\end{minipage}
\caption{Code to square each member of an array.}
\label{fig:squarearray}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{0.7\textwidth}
% \begin{figure}[h]
\begin{code}
int sq\_arr(Share A[]) {
    B = MUL\_N(A, A);
    return B;
}
\end{code}
% \end{figure}
\end{minipage}
\caption{Simple MPC transformation to square an array.}
\label{fig:squarearraympc}
\end{figure}
